Digital History in Finland, 1488-1828

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

```{r publishers-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}

# Unique publishers
df <- df0
# Indicator Finland yes/no
df$Finland <- (df$country == "Finland")

@@

# Unique publication places
df <- df0
df <- df %>%
        filter(catalog == "Fennica" & country == "Finland") %>%
        filter(publication_year >= 1640 & publication_year < 1828) %>%	
        select(publication_decade, publication_place)
npub <- unique(df) %>% group_by(publication_decade) %>% tally()
theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_point(size = 5) +
       geom_line(col = "black") +       
       geom_smooth(col = "black") + 
       xlab("Publication year") +
       ylab("Unique publication places (n)") +        
       ggtitle("Unique publication places in Finland (Fennica)")
print(p)
```

>>>>

```{r publishers-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
# Unique publishers
df <- df0
# Indicator Finland yes/no
df$Finland <- (df$country == "Finland")

@@

# Unique publication places
df <- df0
df <- df %>%
        filter(catalog == "Fennica" & country == "Finland") %>%
        filter(publication_year >= 1640 & publication_year < 1828) %>%	
        select(publication_decade, publication_place)
npub <- unique(df) %>% group_by(publication_decade) %>% tally()
theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_point(size = 5) +
       geom_line(col = "black") +       
       geom_smooth(col = "black") + 
       xlab("Publication year") +
       ylab("Unique publication places (n)") +        
       ggtitle("Unique publication places in Finland (Fennica)")
print(p)

# Places in Fennica Finland 1770
#unique(subset(df0, catalog == "Fennica" & publication_decade == 1770 & country == "Finland")$publication_place)
```

```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, out.width="800px"}
df <- df0
df <- df %>%
        filter(catalog == "Fennica" & country == "Finland") %>%
        filter(publication_year >= 1640 & publication_year < 1828)

# Top publication places
ntop <- 10
top <- names(top(df, "publication_place", ntop))

df <- df %>%	
        filter(publication_place %in% top) %>%	
        select(publication_decade, publication_place, publisher)

npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
npub$publication_place <- factor(npub$publication_place, levels = top)
theme_set(theme_bw(20))

p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", aes(fill = publication_place)) + 
       #geom_point(size = 5, aes(shape = publication_place)) +
       #geom_line(col = "black", aes(shape = publication_place)) +       
       # geom_smooth(col = "black", aes(shape = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +        
       ggtitle("Unique publishers in top publication places (Finland/Fennica)")
print(p)
```
